Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-14 prop_letter.tex
small things

To formalize this connection between QIVPMs and classical IVPMs, we
first note that contrary to the case with conventional quantum
probability spaces, there is generally no unique state $\rho$
consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$ is consistent
with a state $\rho$ and projector $P$ if the interval $\bar{\mu}(P)$
contains the exact probability calculated by the Born rule, i.e, if:
\begin{equation}
\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event~$P$ happens determined by the Born
rule~\citep{Born1983,peres1995quantum,544199}.

@@

The theorem follows directly from our correspondence and Shapley's
theorem that proves that a classical IVPM always contains at least one
state that is consistent with every
event~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}. As we will
illustrate in the next section, the set of states
$\coreBorn\left(\bar{\mu},\events'\right)$ consistent with some events
$\events'$ and a particular QIVPM $\bar{\mu}$ may be
\emph{empty}.

>>>>

To formalize this connection between QIVPMs and classical IVPMs, we
first note that in contrast to the case with conventional quantum
probability spaces, there is generally no unique state $\rho$
consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$ is consistent
with a state $\rho$ and projector $P$ if the interval $\bar{\mu}(P)$
contains the exact probability calculated by the Born rule, i.e, if:
\begin{equation}
\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event~$P$ happens determined by the Born
rule~\citep{Born1983,peres1995quantum,544199}.

@@

The theorem follows directly from our correspondence and Shapley's
theorem that proves that a classical IVPM always contains at least one
state that is consistent with every
event~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}. As we will
illustrate in the next section, the set of states
$\coreBorn\left(\bar{\mu},\events'\right)$ that is consistent with
some events $\events'$ and a particular QIVPM $\bar{\mu}$ may be
\emph{empty}.
